---
title: "Double or Drain"
output: html_document
date: "2025-12-31"
---

```{r setup, include=FALSE}
# This document is for PUBLISHING ONLY.
# Interactive code (readline) must NOT execute during knitting.
library(tidyverse)
```
## What is Double or Drain?

Double or Drain is a probability-based console game about risk and decision-making.

You start with $1. Each round you choose one of three actions:

D — attempt to double your money with probability p

B — bank your current balance and end the game

E — toggle a hint that estimates whether continuing is sensible

If a double attempt fails, your balance becomes $0 and the game ends immediately.

## How to play the game

This webpage does not run the game.

The game is interactive and must be played in the R console.

To play locally, run the following commands in R:




```{r, eval=FALSE}

source("game.R")
play_game(p = 0.6, target = 16)
```

## About the hint

The hint does not maximize expected value.

Instead, it estimates the probability of reaching a chosen target before busting.
This corresponds to a median-style decision rule, not EV maximization.

This illustrates an important concept in probability:

Maximizing expected value can recommend extreme risk-taking, while optimizing for typical outcomes produces a natural stopping rule.
